\subsection{Category and Author Pachinko}\label{app:cat_auth_pachinko}
Given the good results of the taxonomy \gls{pam}, we decided to test \gls{pam} with the two other metadata fields: Author and Category.
These metadata are not layered and can therefore not utilize the layered nature of \gls{pam} in the same way.
Instead, a four-layer \gls{pam} will be used, with a root layer, a metadata layer where words are locked into topics using the technique outlined in \autoref{sec:appendix/locking}, a layer with 90 'blank' topics, and a word layer.

As can be seen from the results in \autoref{tab:cat_auth_pachinko_results}, these models achieve better results than the previous author and category models and the \gls{lda} model.
However, the taxonomy \gls{pam} is still better overall.
The same conclusion is reached after manual inspection of the topics of these models.

\begin{table}[h]
	\centering
	\caption{Topic Coherence ($C_v$) comparison of author and category \gls{pam} (marked with bold) and previous models.}
	\begin{tabular}{l|c}
		Topic Model & \makecell{Topic \\ Coherence} \\
		\midrule
		\acrfull{lda} model & 0.520 \\
		Author-Topic \acrlong{lda} model & 0.335 \\
		Category-Topic \acrlong{lda} model & 0.370 \\
		Taxonomy \acrlong{pam} & 0.660 \\
		\textbf{Author \acrlong{pam}} & \textbf{0.598} \\
		\textbf{Category \acrlong{pam}} & \textbf{0.585} \\
		\textbf{\acrlong{pam}} & textbf{0.670}
	\end{tabular}
	\label{tab:cat_auth_pachinko_results}
\end{table}

For comparison we also ran a four-level \gls{pam} without any metadata, using 100 and 90 as the sizes of the two middle layers.
This ended up providing very good results, slightly better than the Taxonomy \gls{pam}.
This also shows that while Category \gls{pam} and Author \gls{pam} get better results than their \gls{lda} counterparts, it is better to run \gls{pam} without modifications.
This could be due to our application, but it might also point towards these two particular metadata fields not being particularly useful in this specific application.
The category metadata are generally very vague and some categories have seemingly no connection between documents.
And as we have discussed earlier author metadata might not be as usefull within journalism as authors don't write about the same topics as much as with scientific papers.
And while the \gls{pam} without metadata does achieve better topic coherence than the Taxonomy \gls{pam}, they are close enough in both topic coherence and manual inspection of the quality of topics that no conclusions can be drawn.
It could be that Taxonomy \gls{pam} only needed more training time as it is a five level model which increases the training time and complexity significantly compared to the four level model.
