\subsubsection{Metadata labels}\label{sec:appendix_meta_data}
Here are the 58 different categories, which make up all the category labels present within the dataset.

As mentioned in \autoref{sec:dataset}, some nonsensical categories are worth mentioning.
Specifically, the categories '26. Frederik' and '53. Frederik' do not from their names indicate what they cover, since Frederik is simply a normal Danish name.
Since they are not filtered into the 'misc' category during preprocessing, it is worth looking into what documents have these categories.

By looking at a random selection of documents from these categories, there is no clear pattern to be found.
The topics, within these categories, can be about anything from sports to news from anywhere around the world or locally in Denmark.
The articles from '26. Frederik' appear all years in our dataset, while the articles for '53. Frederik' seem to be just from 2019, the last year in our dataset, but evenly distributed over the whole year.
Curiously enough, most of the documents from these categories seem to be written by Anders Kjærgaard, with only a few other authors.
For '26. Frederik' there are just 5 unique authors: Carsten Tolbøll, Emil Abkjær Kristensen, Morten Kyndby Holm, Jens Fogh-Andersen, and Anders Kjærgaard.
For '53. Frederik' there are just 4 unique authors: Klaus Færch Gjerulff, Morten Kyndby Holm, Jens Fogh-Andersen, and Anders Kjærgaard.
This shows that Morten Kyndby Holm, Jens Fogh-Andersen, and Anders Kjærgaard have written for both categories.

From the exploration of these two categories, we can not say with certainty why these categories exist, or why multiple authors have chosen to write for these categories.
We continue to use these categories in our experiment, for the possibility of making other observations through the topic models.

\begin{table*}[h]
	\centering
	\begin{tabular}{l|c|l|c|l|c|l|c}
		Category            & Number & Category        & Number & Category                       & Number & Category                    & Number \\
		\toprule
		Fælles              & 20204  & Navne           &  3749  & Kram                           &  244   & \textbf{Østvendsyssel Avis} &   4    \\
		Thisted-avis        & 11473  & Kultur          &  3012  & 53. Frederik                   &  203   & \textbf{DF Motor Biler}     &   3    \\
		Sport-avis          & 10941  & Morsø Sport     &  2350  & Feature                        &  188   & \textbf{Nyhedsmotoren-net}  &   3    \\
		Debat               & 10075  & Friii           &  2333  & \textbf{Aalborg:nu}            &   73   & \textbf{Plus Publicering}   &   3    \\
		Udland-avis         &  8855  & Bagside         &  1933  & \textbf{Erhvervsnavne}         &   39   & \textbf{RB}                 &   3    \\
		Erhverv-avis        &  7356  & MitLiv          &  1519  & \textbf{Newspack}              &   35   & \textbf{Sport-net}          &   3    \\
		Mariagerfjord-avis  &  7241  & WEEKEND         &  1493  & \textbf{DF Søfart}             &   32   & \textbf{Thisted-net}        &   3    \\
		Morsø-avis          &  5959  & Bo Godt         &  1447  & \textbf{Morsø Ugeavis}         &   27   & \textbf{Hanbo-bladet}       &   2    \\
		Aalborg-avis        &  5544  & Nordjyske Biler &  1400  & \textbf{DF Licitation Byggeri} &   14   & \textbf{Brugermappe}        &   1    \\
		Vesthimmerland-avis &  5131  & Morsø Debat     &  1375  & \textbf{Biler}                 &   13   & \textbf{Brønderslev-net}    &   1    \\
		Rebild-avis         &  4415  & Frieord         &  1341  & \textbf{Samfund}               &   9    & \textbf{Lokalavisen}        &   1    \\
		Frederikshavn-avis  &  4325  & Indsigt         &  984   & \textbf{Nordjyske Plus}        &   6    & \textbf{Mariagerfjord-net}  &   1    \\
		Hjørring-avis       &  4235  & Thisted sport   &  698   & \textbf{Oplandsavisen}         &   6    & \textbf{Morsø-net}          &   1    \\
		Brønderslev-avis    &  3857  & Perspektiv      &  613   & \textbf{INFOMAKER PRINT}       &   5    &                             &        \\
		Jammerbugt-avis     &  3791  & 26. Frederik    &  484   & \textbf{DF Licitation Diverse} &   4    &                             &        \\
		\bottomrule
	\end{tabular}
	\caption{Amount of documents for each of the 58 categories within the Nordjyske dataset from 2017 to 2019.
		The highlighted categories are filtered and combined during preprocessing.}
	\label{tab:category_table}
\end{table*}
