\subsection{Overview}\label{sec:overview}
This section describes the steps of our method on an abstract level.
\autoref{fig:process_figure} visualizes these steps as a flowchart.
The method takes a corpus as an input and produces evaluation results as output.
Each step of the method is described in more detail in the paper.

\subsubsection*{Step 1: Preprocessing phase}
In this step, we apply different preprocessing methods to simplify the dataset and remove redundant information.
Details of this phase are given in \autoref{sec:dataset}.
After finishing this phase, we are left with $139,060$ articles and $69,192$ unique words to form the corpus, which is used in the following steps.

\subsubsection*{Step 2: Training topic models}
In this step, we train the standard \gls{lda} model, and the category, author, and taxonomy metadata models, on the corpus.
The standard \gls{lda} model and the metadata models are described in \autoref{sec:plate_notation}.
The models are trained based on topic coherence, and after the training process, the models are evaluated further.

\subsubsection*{Step 3: Evaluation of topic models}
In this step, we set up an evaluation for the topic models trained in the previous step.
The primary evaluation metric chosen for the experiment is topic coherence, and this is calculated for all of the models.
We also analyze the generated topics to get a deeper understanding of what the models learn.
The evaluation and results are presented in \autoref{sec:experiment} and are analyzed and discussed in \autoref{sec:discussion}.

\input{figures/overview_figure.tex}
